---
output: 
  md_document:
    variant: gfm
---

### NOBA Cod atlantisom2ss conversion
#### Workflow
- Put `NOBA_sacc_30` folder (Atlantisom output) in the `NOBA_cod_files/` folder

- Modify `NOBA_cod_files/Rscript/NOBACOD_atlantisom2SS.R` to convert Atlantisom output to SS input. The NOBACOD_atlantisom2SS.R helps generate SS input files for the NOBA_cod_files/output/atlanis2ss scenario. For scenarios that use depletion-based reduction analysis (NOBA_cod_files/output/atlantis2ss_depletion) and consider initial equilibrium catch (NOBA_cod_files/output/atlantis2ss_initial_equilibrium_catch), we modified the input data following the instructions from the [Stock Synthesis User Manual}(https://nmfs-stock-synthesis.github.io/ss-documentation/SS330_User_Manual.html). 

- We explored five scenarios and the Stock Synthesis input files for each scenario can be found under NOBA_cod_files/output folder

  - atlantis2ss_full_data that uses fishery and survey age composition data. Model had strong patterns in age composition residuals and large final gradient value of 6.88787e+08. The estimation model did not converge after trying different stock-recruitment models, input values of steepness and standard deviation of the recruitment deviation in log space, and selectivity patterns.

  - atlantis2ss_surveyagecomp that uses survey age composition data but not fishery age composition data. Model still did not fit well. 

  - atlantis2ss that uses fishery age composition data but not survey age composition data. Model had a better final gradient value and fit. The expected landings, landing age compositions, and survey indices match well with the true values from Atlantis. However, the estimated biomass, spawning stock biomass, recruitment, and fishing mortality still did not line up with the true values from Atlantis.
  
  - atlantis2ss_depletion that adds another survey fleet that takes SSB as its input. The target depletion was set to 0.5 in the end year. Rick Methot thinks this feature should routinely be used in all SS3 configurations. Rick's insights: 
    - The data show near constant catch for the entire time series and the survey also shows little trend. So little surprise that scale is hard to get right.
    - Given that your model has no initial equilibrium catch (catch with year = -999), the SS3 model time series is assuming that the population is virgin in the start year (40).
    - Then with no trend in the index data, SS3 is getting all scale info from the composition data.  But the composition data show 70% of the fish in the first age bin, beginning in 40.  So there is no contrast here either.  It seems the Atlantis is generating a population that is already highly depleted by year 40, then SS3 starts in year 40 and is told that the population is virgin going into year 40. Please see thoughts from Rick and Ian Taylor from [the post on SS3 public forums](https://vlab.noaa.gov/web/stock-synthesis/public-forums/-/message_boards/message/19365724?_com_liferay_message_boards_web_portlet_MBPortlet_orderByCol=modified-date&_com_liferay_message_boards_web_portlet_MBPortlet_scStart=0&_com_liferay_message_boards_web_portlet_MBPortlet_delta=50&_com_liferay_message_boards_web_portlet_MBPortlet_orderByType=desc&_com_liferay_message_boards_web_portlet_MBPortlet_index=0&_com_liferay_message_boards_web_portlet_MBPortlet_scEnd=50&_com_liferay_message_boards_web_portlet_MBPortlet_resetCur=false&_com_liferay_message_boards_web_portlet_MBPortlet_categoryId=971356&_com_liferay_message_boards_web_portlet_MBPortlet_cur1=1).
  
  - atlantis2ss_initial_equilibrium_catch that has initial equilibrium catches in the data.ss and a short parameter setup line (fishing mortality) for initial equilibrium catches in the control.ss. 

The figures below show comparisons among Atlantis true values, output values from the atlantis2ss_depletion scenario S1, and output values from the atlantis2ss_initial_equilibrium_catch scenario S2 (work in progress). Will make a pull request and move everything back to Sarah's repository after talking to Cecilie.  

```{r, warning = FALSE, message = FALSE, fig.height = 6, echo=FALSE}
# remotes::install_github("r4ss/r4ss")
library(r4ss)
library(here)
library(tidyr)
require(dplyr)
library(ggplot2)
library(ggforce)
library(ggthemes)

# SS output ---------------------------------------------------------------

# SS output path
mydir <- here("NOBA_cod_files", "output")
# read the model output and print diagnostic messages 
ss_depletion <- SS_output(dir = file.path(mydir, "atlantis2ss_depletion"), 
                     verbose = FALSE,
                     printstats = FALSE)
ss_initial_equilibrium_catch <- SS_output(dir = file.path(mydir, "atlantis2ss_initial_equilibrium_catch"), 
                     verbose = FALSE,
                     printstats = FALSE)

# plots the SS results
# SS_plots(ss_depletion)
# SS_plots(ss_initial_equilibrium_catch)


# Atlantis output ---------------------------------------------------------
# Set up d.name and scenario.name
d.name <- here::here("NOBA_cod_files", "NOBA_sacc_30")
scenario.name <- "nordic_runresults_01"

# Atlantis OM truth data
truth <- get(load(file.path(file.path(d.name, "nordic_runresults_01run_truth.RData"))))
omlist_ss <- readRDS(file=file.path(d.name, "nordic_runresults_01omlist_ss.rds"))

# Set species name
species <- c("North_atl_cod")
species_code <- "NCO"

# Number of years of data to pull (From the project page: https://sgaichas.github.io/poseidon-dev/NOBAcod2.html#)
nyears <- omlist_ss$runpar$nyears #144

# Atlantis initialization period in years
burnin <- 0

# fishery output: learned the hard way this can be different from ecosystem outputs
fstepperyr <- if(omlist_ss$runpar$outputstepunit=="days") 365/omlist_ss$runpar$toutfinc #5

noutsteps <- omlist_ss$runpar$tstop/omlist_ss$runpar$outputstep #720
timeall <- c(0:noutsteps)
stepperyr <- if(omlist_ss$runpar$outputstepunit=="days") 365/omlist_ss$runpar$toutinc #5
midptyr <- round(median(seq(0,stepperyr))) #2

timestep <- stepperyr #5

#The last timestep to sample
total_sample <- noutsteps-1 #719
# same time dimensioning parameters as in surveycensus.R
#Vector of indices of catch in numbers to pull (by timestep to sum)
fish_sample_full <- c(0:total_sample)  #total_sample defined in sardinesurvey.R #0-719
fish_burnin <- burnin*fstepperyr+1 #1
fish_nyears <- nyears*fstepperyr #144*5=720
fish_times <- fish_sample_full[fish_burnin:(fish_burnin+fish_nyears-1)] #0-719
fish_timesteps <- seq(fish_times[fstepperyr], max(fish_times), by=fstepperyr) #last timestep: 4, 9, ...719
#fish_years <- unique(floor(fish_times/fstepperyr)+1) # my original [1-144]
fish_years <- unique(floor(fish_times/fstepperyr)) #from Christine's new sardine_config.R [0-143]

fishtime <- fish_times #0-719


fitstartyr <- 40
fitendyr <- 79  #Fishery catch-at-age and weight-at-age data year range: 30-79

#Number of years of data to pull
nyears <- omlist_ss$runpar$nyears #144
total_sample <- omlist_ss$runpar$tstop/omlist_ss$runpar$outputstep #720
stepperyr <- if(omlist_ss$runpar$outputstepunit=="days") 365/omlist_ss$runpar$toutinc #5

atlantis_full <- c(0:total_sample)  
mod_burnin <- fitstartyr*stepperyr+1 #201
fit_nyears <- fitendyr-fitstartyr+1 #40
fit_ntimes <- fit_nyears*stepperyr #200
fittimes <- atlantis_full[mod_burnin:(mod_burnin+fit_ntimes-1)] #200-399
fit_timesteps <- seq(fittimes[stepperyr], max(fittimes), by=stepperyr) #last timestep
fit_years <- unique(floor(fittimes/stepperyr)) #from Christine's new sardine_config.R #40-79
fittimes.days <- fittimes*73 #14600, 14673, ...29127


# Comparisons -------------------------------------------------------------

folder_path <- here("atlantisoutput", "NOBA_sacc_30")

# Fall biomass
fallB <- readRDS(file.path(d.name, paste0(scenario.name,"_BTS_fall_allbox_effic1surveyB.rds")))

fallB_ss <- fallB[[1]] %>%
  filter(species == "North_atl_cod")

plotB <-ggplot() +
  geom_line(data=fallB_ss, aes(x=(time-3)/stepperyr,y=atoutput, color="True fall survey B"), 
            alpha = 10/10) +
  geom_point(data=ss_depletion$cpue[which(ss_depletion$cpue$Fleet==2),], aes(x=Yr,y=Exp*1000, color="SS3 S1 Est B"),
             alpha = 10/10) + 
  geom_point(data=ss_initial_equilibrium_catch$cpue[which(ss_initial_equilibrium_catch$cpue$Fleet==2),], aes(x=Yr,y=Exp*1000, color="SS3 S2 Est B"),
             alpha = 10/10) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name) 

plotB +
  facet_wrap(~species, scales="free") 


# Spring biomass
springB <- readRDS(file.path(d.name, paste0(scenario.name,"_BTS_spring_allbox_effic1surveyB.rds")))

springB_ss <- springB[[1]] %>%
  filter(species == "North_atl_cod")

plotB <-ggplot() +
  geom_line(data=springB_ss, aes(x=(time-1)/stepperyr,y=atoutput, color="True spring survey B"), 
            alpha = 10/10) +
  geom_point(data=ss_depletion$cpue[which(ss_depletion$cpue$Fleet==3),], aes(x=Yr,y=Exp*1000, color="SS3 S1 Est B"),
             alpha = 10/10) + 
  geom_point(data=ss_initial_equilibrium_catch$cpue[which(ss_initial_equilibrium_catch$cpue$Fleet==3),], aes(x=Yr,y=Exp*1000, color="SS3 S2 Est B"),
             alpha = 10/10) + 
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

plotB +
  facet_wrap(~species, scales="free") 

# Landings
trueL <- read.table(file.path(folder_path, "nordic_runresults_01Catch.txt"), header = TRUE)
trueL_ss <- trueL[which(as.integer(trueL$Time/365) %in% fit_years), species_code]

ssL1 <- ss_depletion$timeseries$`sel(B):_1`[ss_depletion$timeseries$Yr %in% fit_years]*1000
ssL2 <- ss_depletion$timeseries$`sel(B):_1`[ss_initial_equilibrium_catch$timeseries$Yr %in% fit_years]*1000

plot(trueL_ss, ylim=range(trueL_ss, ssL1, ssL2), 
     xlab="Year", ylab="Landings (t)")
lines(ssL1, lty=1)
lines(ssL2, lty=2)
legend("topright",
       c("True L", "SS3 S1 Est L", "SS3 S2 Est L"),
       pch=c(1, NA, NA), 
       lty=c(NA, 1, 2),
       bty="n")

# Biomass
trueB <- read.table(file.path(folder_path, "nordic_runresults_01BiomIndx.txt"), header = TRUE)

trueB_ss <- trueB[which(as.integer(trueB$Time/73) %in% fit_timesteps), species_code]

ssB1 <- ss_depletion$timeseries$Bio_all[ss_depletion$timeseries$Yr %in% fit_years]*1000
ssB2 <- ss_initial_equilibrium_catch$timeseries$Bio_all[ss_initial_equilibrium_catch$timeseries$Yr %in% fit_years]*1000

par(mar = c(5, 4, 4, 4) + 0.3) 
plot(trueB_ss, 
     xlab="Year", ylab="True Biomass (t)")
par(new = TRUE)
plot(ssB1, type = "l", axes = FALSE, bty = "n", xlab = "", ylab = "")
lines(ssB2, lty=2)
axis(side=4, at = pretty(range(ssB1, ssB2)))
mtext("SS Est Biomass (t)", side=4, line=3)
legend("topright",
       c("True B", "SS3 S1 Est B", "SS3 S2 Est B"),
       pch=c(1, NA, NA), 
       lty=c(NA, 1, 2),
       bty="n")

# Spawning stock biomass
trueSSB <- read.table(file.path(folder_path, "nordic_runresults_01SSB.txt"), header = TRUE)
trueSSB_ss <- trueSSB[which(as.integer(trueSSB$Time/73) %in% fit_timesteps), species_code]

ssSSB1 <- ss_depletion$timeseries$SpawnBio[ss_depletion$timeseries$Yr %in% fit_years]*1000
ssSSB2 <- ss_initial_equilibrium_catch$timeseries$SpawnBio[ss_initial_equilibrium_catch$timeseries$Yr %in% fit_years]*1000

par(mar = c(5, 4, 4, 4) + 0.3) 
plot(trueSSB_ss, 
     xlab="Year", ylab="True SSB (t)")
par(new = TRUE)
plot(ssSSB1, type = "l", axes = FALSE, bty = "n", xlab = "", ylab = "")
lines(ssSSB2, lty=2)
axis(side=4, at = pretty(range(ssSSB1, ssSSB2)))
mtext("SS Est SSB (t)", side=4, line=3)
legend("topright",
       c("True SSB", "SS3 S1 Est SSB", "SS3 S2 Est SSB"),
       pch=c(1, NA, NA), 
       lty=c(NA, 1, 1),
       bty="n")

# Recruitment

nitro <- merge(omlist_ss$biol$kwsr, omlist_ss$biol$kwrr, by = "1")
names(nitro) <- c("Code", "KWSR", "KWRR")

nitro <- nitro %>%
  group_by(Code) %>%
  mutate(Nsum = sum(KWSR, KWRR))
truerec <- omlist_ss$YOY_ss %>% 
  pivot_longer(-Time, names_to = "Code", values_to = "recwt") %>%
  mutate(Code = gsub("\\.0", "", Code)) %>%
  filter(Time>0) %>% # this output not meaningful
  filter(Time %in% seq(365, max(Time), by=365)) %>%
  left_join(omlist_ss$funct.group_ss[, c("Code", "Name")]) %>%
  left_join(nitro) %>%
  mutate(recnums = (recwt * 50000000.0 / omlist_ss$biol$redfieldcn) / Nsum) %>%
  group_by(Name) %>%
  mutate(meanrecnums = mean(recnums))

truerec_ss <- truerec[truerec$Name==species,]

plotR <-ggplot() +
  geom_line(data=truerec_ss, aes(x=Time/365,y=recnums, color="True R"), 
            alpha = 10/10) +
  geom_point(data=ss_depletion$timeseries, aes(x=Yr,y=(Recruit_0*1000), color="SS3 S1 Est R"),
             alpha = 10/10) +
  geom_point(data=ss_initial_equilibrium_catch$timeseries, aes(x=Yr,y=(Recruit_0*1000), color="SS3 S2 Est R"),
             alpha = 10/10) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

plotR 

ssR1 <- ss_depletion$timeseries$Recruit_0[ss_depletion$timeseries$Yr %in% fit_years]*1000
ssR2 <- ss_initial_equilibrium_catch$timeseries$Recruit_0[ss_initial_equilibrium_catch$timeseries$Yr %in% fit_years]*1000

par(mar = c(5, 4, 4, 4) + 0.3) 
plot(fit_years, truerec_ss$recnums[which((truerec_ss$Time/365) %in% fit_years)], 
     xlab="Year", ylab="True R")
par(new = TRUE)
plot(fit_years, ssR1, type = "l", axes = FALSE, bty = "n", xlab = "", ylab = "")
lines(fit_years, ssR2, lty=2)
axis(side=4, at = pretty(range(ssR1, ssR2)))
mtext("SS Est R", side=4, line=3)
legend("topright",
       c("True R", "SS3 S1 Est R", "SS3 S2 Est R"),
       pch=c(1, NA, NA), 
       lty=c(NA, 1, 2),
       bty="n")

# Fishing mortality
file.mort <- file.path(folder_path, "nordic_runresults_01Mort.txt")

mortish <- read.table(file.mort, header = TRUE)

relF_ss <- mortish %>%
  select(Time, relF = paste0(species_code, ".F"))

names(ss_depletion$timeseries)[19]<-"Fmort"
names(ss_initial_equilibrium_catch$timeseries)[19]<-"Fmort"

plotF <-ggplot() +
  geom_line(data=relF_ss, aes(x=Time/365, y=relF, color="True F"), 
            alpha = 10/10) +
  geom_point(data=ss_depletion$timeseries, aes(x=Yr,y=Fmort, color="SS3 S1 Est F"),
             alpha = 10/10) + 
  geom_point(data=ss_initial_equilibrium_catch$timeseries, aes(x=Yr,y=Fmort, color="SS3 S2 Est F"),
             alpha = 10/10) + 
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

plotF 

ssF1 <- ss_depletion$timeseries$Fmort[ss_depletion$timeseries$Yr %in% fit_years]
ssF2 <- ss_initial_equilibrium_catch$timeseries$Fmort[ss_initial_equilibrium_catch$timeseries$Yr %in% fit_years]
par(mar = c(5, 4, 4, 4) + 0.3) 
plot(fit_years, relF_ss$relF[(relF_ss$Time/365) %in% fit_years], 
     xlab="Year", ylab="True F")
par(new = TRUE)
plot(fit_years, ssF1, type = "l", axes = FALSE, bty = "n", xlab = "", ylab = "")
lines(fit_years, ssF2, lty=2)
axis(side=4, at = pretty(range(ssF1, ssF2)))
mtext("SS Est F", side=4, line=3)
legend("topright",
       c("True F", "SS3 Est F"),
       pch=c(1, NA, NA), 
       lty=c(NA, 1, 2),
       bty="n")

# R over SSB
plot(trueSSB_ss, 
     truerec_ss$recnums[(truerec_ss$Time/365) %in% fit_years],
     xlab="True SSB", 
     ylab="True R")



```

### NOBA Cod SAM2SS conversion
In this example, we convert NOBA Cod State-space assessment model (SAM) inputs to Stock Synthesis (SS) inputs and compare the outputs from the two packages.

#### Install and library packages
```{r, warning = FALSE, message = FALSE}
# install.packages("here")
# 
# install_64bit <- TRUE
# 
# if (install_64bit) {
#   args <- c("--no-multiarch")
# } else {
#   args <- c("")
# }
# 
# devtools::install_github("fishfollower/SAM/stockassessment", INSTALL_opts = args)
# 
# remotes::install_github("r4ss/r4ss", branch = "development")
# 
# remotes::install_github("Bai-Li-NOAA/saconvert") # Need to install "kellijohnson-NOAA/saconvert" after doing pull request.
# 
# remotes::install_github("nmfs-general-modeling-tools/nmfspalette")

library(here)
library(stockassessment) # For using SAM
library(r4ss) # For using SS
library(saconvert)
library(nmfspalette)
```

#### Read SAM input data and run SAM
```{r, warning = FALSE, message = FALSE}
sam_input_path <- here::here("NOBA_cod_files", "NEAcod-2020", "data")

# Read in data files
regdat <- grep(".dat",list.files(sam_input_path))
filenames_ICES <- list.files(sam_input_path)[regdat]

#All objects are now on input_file_list
input_file_list <- lapply(file.path(sam_input_path,filenames_ICES), read.ices)
names(input_file_list) <- gsub(".dat","",filenames_ICES)

#Load into function environment as objects
list2env(input_file_list, environment())

# Create a collected data object
sam_dat <- setup.sam.data(
  surveys = survey,
  residual.fleet = cn,
  prop.mature = mo,
  stock.mean.weight = sw,
  catch.mean.weight = cw,
  dis.mean.weight = dw,
  land.mean.weight = lw,
  prop.f = pf,
  prop.m = pm,
  natural.mortality = nm,
  land.frac = lf
)

# Generate a default/minimalistic model configuration
sam_conf <- defcon(sam_dat)

# Generate default initial values for all our model parameters
sam_par <- defpar(sam_dat, sam_conf)

# Fit the SAM model
sam_fit <- sam.fit(sam_dat, sam_conf, sam_par, silent=TRUE)

```


#### Plot SAM fits
```{r, fig.height = 6, sam_fit}
par(mfrow = c(1, 1))
ssbplot(sam_fit)
fbarplot(sam_fit)
recplot(sam_fit)
catchplot(sam_fit)
```

#### Convert SAM inputs to SS inputs
```{r, warning = FALSE, message = FALSE}
# Set up two scenarios
# Scenario A: use selectivity pattern 20 and F method 3 in SS
# Scenario B: use selectivity pattern 20 and F method 2 in SS

scenario_path <- c("A", "B")
slx_pattern <- c(20, 20)
f_method <- c(3, 2)


for (scenario_id in seq_along(scenario_path)){
  output_path <- here::here("NOBA_cod_files", "output", scenario_path[scenario_id])
  if(!dir.exists(output_path)) dir.create(output_path)
  
  saconvert::ICES2SS(
    user.wd = sam_input_path,
    user.od = output_path,
    ices.id = "",
    tvslx = FALSE,
    ages = NULL,
    nsexes = 1, # 1: one sex; 2: two sex; -1: one sex and multiply the spawning biomass by the fraction female in the control file
    forN = 2,
    q.extra.se = FALSE,
    q.float = FALSE,
    slx = slx_pattern[scenario_id],
    f.method = f_method[scenario_id]
  ) # steep.init: http://sedarweb.org/docs/wpapers/SEDAR19_DW_06_SteepnessInference.pdf
  
}
```

#### Compare SAM outputs and SS outputs
```{r, warning = FALSE, message = FALSE, fig.height = 6, sam_ss_comparison}
sam_output <- data.frame(
  "Year" = c(sam_dat$years),
  "SSB" = exp(sam_fit$sdrep$value[names(sam_fit$sdrep$value) %in% "logssb"]),
  "Recruits" = exp(sam_fit$sdrep$value[names(sam_fit$sdrep$value) %in% "logR"]),
  "F" = exp(sam_fit$sdrep$value[names(sam_fit$sdrep$value) %in% "logfbar"]),
  "Catch" = c(exp(sam_fit$sdrep$value[names(sam_fit$sdrep$value) %in% "logCatch"]), NA)
)

ss_output <- list()
for (scenario_id in seq_along(scenario_path)){
  ss_output_path <- here::here("NOBA_cod_files", "output", scenario_path[scenario_id])
  ss_output_data <- SS_output(dir = ss_output_path, verbose = F, printstats = F)
  ss_output[[scenario_id]] <- data.frame(
    "Year" = sam_output$Year,
    "SSB" = ss_output_data$timeseries$SpawnBio[ss_output_data$timeseries$Yr %in% sam_output$Year],
    "Recruits" = ss_output_data$timeseries$Recruit_0[ss_output_data$timeseries$Yr %in% (sam_output$Year-1)],
    "F" = ss_output_data$timeseries$`F:_1`[ss_output_data$timeseries$Yr %in% sam_output$Year],
    "Catch" = ss_output_data$timeseries$`sel(B):_1`[ss_output_data$timeseries$Yr %in% sam_output$Year]
  )
}

var <- c("SSB", "Recruits", "F", "Catch")
var_label <- c("SSB", "Recruits (Age 3)", expression(F[9-13]), "Catch (in weight)")
colors <- nmfspalette::nmfs_palette("regional web")(length(scenario_path)+1)

par(mfrow = c(2, 2), mar = c(4, 4, 1, 1))

for (i in seq_along(var)){
  plot(NA,
       type="n",
       xlim = range(sam_output$Year),
       ylim = range(sam_output[, var[i]], na.rm = T),
       xlab = "Year",
       ylab = var_label[i]
  )
  lines(sam_output$Year,
        sam_output[, var[i]],
        lty=1,
        col=colors[1])
  for (j in seq_along(scenario_path)){
    lines(ss_output[[j]]$Year,
          ss_output[[j]][, var[i]],
          lty=j+1,
          col=colors[j+1])
  }
}

legend("top", 
       c("SAM", paste("SS_", scenario_path)),
       lty = seq_along(colors),
       col = colors,
       bty="n")
```


### Resources
  - [SAM GitHub repository](https://github.com/fishfollower/SAM)
	- Aldrin et al., 2020: [The specification of the data model part in the SAM model matters](https://www.sciencedirect.com/science/article/pii/S0165783620301028#bib0020)
	- Nielsen and Berg, 2014: [Estimation of time-varying selectivity in stock assessments using state-space models](https://www.sciencedirect.com/science/article/abs/pii/S0165783614000228?via%3Dihub)
	- Berg and Nielsen, 2016: [Accounting for correlated observations in an age-based state-space stock assessment model](https://academic.oup.com/icesjms/article/73/7/1788/2458744)
	- [ICES Report of the Arctic Fisheries Working Group (AFWG)](https://www.ices.dk/sites/pub/Publication%20Reports/Expert%20Group%20Report/acom/2018/AFWG/00-AFWG%202018%20Report.pdf)
	
